### 2025-08-25 Scripts/Manuscript/manuscript.Rmd
adjusted the supplementary materials to reflect the new project structure, fixed references, and removed depricated files.

# loading script with helper functions
# source(file = "../helper_functions.R") !!!needs to still be created

@@

\renewcommand{\arraystretch}{0.7}

<!-- reducing the line spacing within tables -->

\renewcommand{\topfraction}{.8}

<!-- max fraction of page for floats at top -->

\renewcommand{\bottomfraction}{.8}

<!-- max fraction of page for floats at bottom -->

\renewcommand{\textfraction}{.15}

<!-- min fraction of page for text -->

\renewcommand{\floatpagefraction}{.8}

<!-- min fraction of page that should have floats .66 -->

@@

# Function for storing data openly in the analysis data folder
saving_to_analysis_data <- function(data){
  open_data(data = data, filename = paste0(paste0(
    "Data/AnalysisData/", deparse(substitute(data))), ".csv"),
    codebook = NULL, value_labels = NULL) 
}

@@

When we validate a measure using psychometrics, we evaluate it mainly on two aspects: construct validity & reliability. Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in the unobserved constructs of interest between participants (Cronbach & Meehl, 1955; Vazire et al., 2022). Whereas reliability refers to how consistent a participant's responses on a measurement are [@nunnally1978overview; @mellenbergh2011conceptual]. Reliability is part of the validation of a measure because an unreliable measure cannot consistently capture a construct through the items, and therefore cannot be assumed to properly capture the construct of interest (Crutzen & Ygram Peters, 2015). Suppose we have a measure and we want it to measure general intelligence, and we want to validate this as a measure of general intelligence. We would see our measurement as construct valid if being more intelligent resulted in generally scoring higher on our test, and our measurement would be reliable if the score of people on our measure consistently reflected their actual intelligence.

In practice construct validity is often evaluated through factor analysis. In factor analysis, a model is fitted to explain as much of the variance of multiple items through a smaller number of factors, which are each weighted averages of the item scores. The number of factors are first specified, and then the fit of a model involving those number of factors is determined. Preferably, a model with the number of factors corresponding to the number of constructs of interest should show adequate fit. Additionally, the items aimed at the same construct should be statistically related to the same factor. For example, suppose items 1 through 5 from our general intelligence measure are meant to capture verbal intelligence, and items 6 through 10 are distinctly about mathematical intelligence. To establish construct validity, we want to find that a two factor model shows adequate fit, with one factor to which items 1 through 5 relate, and one to which items 6 through 10 relate. However, even in this scenario we cannot be certain that the second factor relates to mathematical intelligence and not for example abstract thinking, other types of validity checks as well as theoretical underpinnings will be necessary. Additionally, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance (Horn et al., 1983; Cheung & Rebecca, 2012).

Reliability gives us an indication of how much our measure captures the signal of our measured variables over noise. Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual]. For example, we can compare scores on multiple equivalent forms of the test, between multiple different raters, or between multiple different timepoints of the same test. Still, the most common way to assess reliability is through an indication of consistency within the measure itself, and the most common among these indicators is the Cronbach's Alpha coefficient. The Cronbach's Alpha coefficient is defined as “the average of all the possible split-half coefficients for a given test” (Cronbach, 1951). Here split-half coefficients being the correlation between two halves of the same test. It can be calculated by taking the ratio of interitem covariance to total variance and multiplying it by n / (n - 1), where n is the number of items in the scale. However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, so a single factor. Furthermore, because Cronbach's alpha is proportional to the total variance in the target variable in the sample, it is an indicator of reliability of a measurement, and not the measure itself. In spite of this many researchers report and interpret Cronbach's Alpha as such (Cortina, 1993; Schmitt, 1996).

Thus, psychometric tests are useful but they are not always easy to perform in practice. Even simple factor analysis requires sample sizes of at least around 100, unless the amount of variance explained by the factors is large and the factor structure is clear (Gorsuch, 1983; MacCallum et al., 1999). However, even in the latter case factor analysis does not converge with low sample sizes. Furthermore, if we want to know not just the reliability and validity of one measurement but for the measure across multiple contexts, we need to conduct multiple studies with approximately 400 people per group to detect meaningful effects (Meade & Bauer, 2007; French & Finch, 2016; Koziol & Bovaird, 2018). However, what we observe in the literature is that most measures are reused once or never (THE NOT HUSSEY PAPER ABOUT TOOTHBRUSH MEASURES; also the other Hussey paper with the blocks). Finally, \@shaw2020measurement checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@klein2018many] on the available data, the results. They observed that for none of the scales they assessed, a factor structure congruent with the use of the scales met all of their evaluation criteria, and reliability was rarely consistently above an acceptable threshold.

@@

As illustrated in the previous section, validating measurement is a complex but essential part of doing psychological research. Yet the scientific community has not fully stepped up to this challenge (FLAKE & FRIED 2020). A large number of measures used in the psychological literature lack information on the validity and reliability of the measure (Hogan & Agnello, 2004; Flake et al., 2017; Flake et al., 2022).

Questionable Measurement Practices (QMPs) are practices that raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs; @simmons2011false; @john2012measuring; @wicherts2016degrees]. QMPs range from lack of transparency in the reporting of the measure and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement]. @flake2022construct documented QMPs among 100 replications and their respective original articles from the Reproduciiblity Project Psychology [@osc2015estimating]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Additionally, only eight of the 40 translated scales contained validity evidence for the translated version. But reporting of reliability and validity evidence is not only low, but may also be biased as well. !!!HUSSEY et al., 2023/2025!!! observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and low reporting just below .70. Thus the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.

Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also show that QMPs not only limit the reported validity of a measurement in a study, the lack of information also creates challenges for replicating researchers. Basic content descriptions such as the number of items, the response format, the scoring of the scale were irregular (exact numbers). If it is not clear what items were used, how they were scored, and how they were administered, then it is challenging to reconstruct the measurement for a replication study. In turn, the replication may assess the constructs in a substantially similar way, or they even assess different constructs. If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original. If constructs are assessed differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study. In either case, substantial comparisons between original and replication are hindered.

@@

Our aim is to provide a descriptive account of the reliability, validity, and reporting practices of measurement in replications and related original research. We coded several aspects of the measurement reporting practices in replications and original articles. Additionally, we estimated the reliability and validity evidence using openly available replication data of the measurement item responses from across multiple labs. Our unique contribution is by evaluating reported and the recalculated measurement information for each measure together. This allows us to capture a "double whammy" scenario where there is uncertainty in the reliability and validity of these measures when we calculate these ourselves, and where QMPs obscure the ability to evaluate the measure as well as inhibiting future researchers to recreate the measurement to validate it in a new study. Besides this, our study also functions as a conceptual replication of earlier research looking at reporting practices and measurement validation using different questions and analyses on a different set of replications and original research. While the theory underlying the measurement is important to evaluate how the content of the measure fits to the constructs of interest, because evaluating the theory of a measurement requires domain specific knowledge for each measure we do not address it in this study, we refer interested readers to articles discussing theory in measurement elsewhere (Gehlbach & Brinkworth, 2011; Humphry, 2017; Borgstede and Eggert, 2023; Hasselman, 2023).

# Disclosures ???Where & How???

@@

The data consists of three main sources: replication datasets, replication protocols, and original study articles. We retrieved the data of Many Labs 1, 2, 3, & 5 [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] from their respective OSF pages. Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the coding protocol information file in the supplementary materials.

@@

### Saving to Intermediate Data Folder
### !!!! OMIT INTERMEDIATE DATA & KEEP FUNCTION THAT REMOVE ALL NON RAW DATA 
### WHEN LOADING THE DATA IN!!!!
saving_to_intermediate_data(data_1.3_clean)
saving_to_intermediate_data(data_1.10_clean)
saving_to_intermediate_data(data_1.11_clean)
saving_to_intermediate_data(data_1.12.3.1_clean)
saving_to_intermediate_data(data_1.12.3.2_clean)
saving_to_intermediate_data(data_2.10.1_clean)
saving_to_intermediate_data(data_2.12.1_clean)
saving_to_intermediate_data(data_2.12.2_clean)
saving_to_intermediate_data(data_2.12.3_clean)
saving_to_intermediate_data(data_2.15_clean)
saving_to_intermediate_data(data_2.20_clean)
saving_to_intermediate_data(data_2.23_clean)
saving_to_intermediate_data(data_3.2.1.1_clean)
saving_to_intermediate_data(data_3.2.1.2_clean)
saving_to_intermediate_data(data_3.7.1_clean)
saving_to_intermediate_data(data_3.7.2_clean)
saving_to_intermediate_data(data_3.8.2_clean)
saving_to_intermediate_data(data_5.1.1_clean)
saving_to_intermediate_data(data_5.1.2_clean)
saving_to_intermediate_data(data_5.4_clean)
saving_to_intermediate_data(data_5.7_clean)
saving_to_intermediate_data(data_5.9.1_clean)

@@

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of the replication of an original study. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the data retrieval information XXX supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).

@@

We extracted reported measurement information from the original articles and replication protocols using our preregistered coding protocol. We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) when present. Similarly, we coded if any psychometric construct validity evidence, such as a factor analysis, was presented for the measure. We additionally included twenty items that were based on the QMP table presented in Flake & Fried (2020). For each of these items we a piece information we would want to see reported with regards to the measurement was described. If the information was clearly reported we coded the item as true; false if not or not clear enough; or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures). Example items can be seen in Table 1.

@@

After the initial coding, we made minor revisions to 14 of the 20 QMP items from the preregistered coding protocol. These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent in the exact way and degree of detail in which to present things. For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables, and figures presented in this article are all based on the revised coding protocol. The results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in Supplementary Analyses D.

We initially intended to form a QMP index using these QMP items and perform regression analyses using this index, but this index could not be validated properly and its results would be misleading to present here. A more detailed explanation of what was omitted and why, as well as the results from the preregistered analyses themselves can be found in Supplementary Materials XXX. The items are currently used as individual descriptives on the reporting practices in our sample.

@@

We calculated reliability for each measure from the replication datasets with suitable data for each lab the measure was used in. We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from Duhachek and Lacobucci (2004) to calculate the standard error in the meta-analysis. Then we entered these two values into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis (Botella & Suero, 2012; López-Ibáñez et al., 2024; Vacha-Haase, 1998). Using RG Meta-Analysis we quantified the degree of true variation (or heterogeneity) in reliability coefficients across lab locations. We performed the RG Meta-Analysis using the rma function from the metafor R package (v4.4-0; Viechtbauer, 2010) and default settings. We evaluated the heterogeneity using the tau statistic and the Cochran's Q-test (CITATION Cochran 1954). These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low (Hoaglin 2015; Pereira et al. 2010). Therefore, we also present the prediction interval and suggest that the heterogeneity results should be viewed with a critical eye (Borenstein 2024 CITATION). We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

Our analyses will focus on Cronbach’s Alpha, because its common use in research allows us to make comparisons between calculated and reported reliabilities. Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis. We additionally estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha, while also simultaneously providing some validity evidence [@crutzen2017scale; @deng2017testing]. McDonald’s Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1. No RG Meta-Analysis was performed on McDonald's Omega, as we could not find a formula for calculating its standard error.

@@

We tested for unidimensionality using two tests on the data from each lab for each measure. If at least one of these tests was passed, the measure in that lab was marked as unidimensional. For the first test we fit a Confirmatory Factor Analysis (CFA) model with one factor to the data, and we then evaluate the RMSEA value. If this value is below .08, the test is passed. For the second test we run a parallel analysis. This runs multiple Exploratory Factor Analyses (EFA) where the number of factors in the model is increased by 1 until the number of factors is one less than the number of items. It then compares the eigenvalues (an indication of how much variance is explained by that factor) of each factor to the eigenvalues for that factor if the data matrix was effectively random. If only the single factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed. We chose a combination of these two tests, as the RMSEA is known to be biased for models with small degrees of freedom (Kenny et al., 2015), while the parallel analysis may be less suited if a two or more factor solution would also fit the sample item data.

@@

The average calculated Cronbach’s alpha coefficient across individual replications was `r apa_num(mean(calculated_reliability_lab_data$alpha))` with a standard deviation of `r apa_num(sd(calculated_reliability_lab_data$alpha))`. Figure 2 displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication, based on the meta-analytic p-value (alpha \< .05) retrieved from the Many Labs reports.

@@

```{r plot_alpha_distributions, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated. Cronbach's alpha values that fell below 0 were excluded. The green lines indicate the meta-analytic prediction interval lower and upper bound. The blue triangles indicate the reported alpha coefficient for that measure from the original article, when reported. The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure. Meta-analyses for which the Q-test for heterogeneity was significant at alpha < .05 are in black, while non-significant results are in grey. The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures. The reported reliabilities that fell outside the 95% quantile of calculated reliability scores are shown in black, otherwise in grey."}

>>>>

@@

\renewcommand{\arraystretch}{0.7} <!-- reducing the line spacing within tables -->

\renewcommand{\topfraction}{.8} <!-- max fraction of page for floats at top -->

\renewcommand{\bottomfraction}{.8} <!-- max fraction of page for floats at bottom -->

\renewcommand{\textfraction}{.15} <!-- min fraction of page for text -->

\renewcommand{\floatpagefraction}{.8} <!-- min fraction of page that should have floats .66 -->

@@

# Function for storing data openly in the analysis data folder
saving_to_analysis_data <- function(data){
  open_data(data = data, filename = paste0(paste0(
    "Data/AnalysisData/", deparse(substitute(data))), ".csv"),
    codebook = NULL, value_labels = NULL) 
}
```

@@

When we validate a measure using psychometrics, we evaluate it mainly on two aspects: construct validity & reliability. Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in the unobserved constructs of interest between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022]. Whereas reliability refers to how consistent a participant's responses on a measurement are [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. Reliability is part of the validation of a measure because an unreliable measure cannot consistently capture a construct through the items, and therefore cannot be assumed to properly capture the construct of interest [@crutzenScaleQualityAlpha2017b]. Suppose we have a measure and we want it to measure general intelligence, and we want to validate this as a measure of general intelligence. We would see our measurement as construct valid if being more intelligent resulted in generally scoring higher on our test, and our measurement would be reliable if the score of people on our measure consistently reflected their actual intelligence.

In practice construct validity is often evaluated through factor analysis. In factor analysis, a model is fitted to explain as much of the variance of multiple items through a smaller number of factors, which are each weighted averages of the item scores. The number of factors are first specified, and then the fit of a model involving those number of factors is determined. Preferably, a model with the number of factors corresponding to the number of constructs of interest should show adequate fit. Additionally, the items aimed at the same construct should be statistically related to the same factor. For example, suppose items 1 through 5 from our general intelligence measure are meant to capture verbal intelligence, and items 6 through 10 are distinctly about mathematical intelligence. To establish construct validity, we want to find that a two factor model shows adequate fit, with one factor to which items 1 through 5 relate, and one to which items 6 through 10 relate. However, even in this scenario we cannot be certain that the second factor relates to mathematical intelligence and not for example abstract thinking, other types of validity checks as well as theoretical underpinnings will be necessary. Additionally, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].

Reliability gives us an indication of how much our measure captures the signal of our measured variables over noise. Psychometrics offers various ways to assess reliability empirically [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. For example, we can compare scores on multiple equivalent forms of the test, between multiple different raters, or between multiple different timepoints of the same test. Still, the most common way to assess reliability is through an indication of consistency within the measure itself, and the most common among these indicators is the Cronbach's Alpha coefficient. The Cronbach's Alpha coefficient is defined as “the average of all the possible split-half coefficients for a given test” [@cronbachCoefficientAlphaInternal1951]. Here split-half coefficients being the correlation between two halves of the same test. It can be calculated by taking the ratio of interitem covariance to total variance and multiplying it by n / (n - 1), where n is the number of items in the scale. However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, so a single factor. Furthermore, because Cronbach's alpha is proportional to the total variance in the target variable in the sample, it is an indicator of reliability of a measurement, and not the measure itself. In spite of this many researchers report and interpret Cronbach's Alpha as such [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].

Thus, psychometric tests are useful but they are not always easy to perform in practice. Even simple factor analysis requires sample sizes of at least around 100, unless the amount of variance explained by the factors is large and the factor structure is clear (Gorsuch, 1983; MacCallum et al., 1999). However, even in the latter case factor analysis does not converge with low sample sizes. Furthermore, if we want to know not just the reliability and validity of one measurement but for the measure across multiple contexts, we need to conduct multiple studies with generally even larger sample sizes per group to detect meaningful effects [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018]. However, what we observe in the literature is that most measures are reused once or never [@elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025]. Finally, @maireadshawMeasurementPracticesLargescale2020 checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@kleinManyLabs22018b] on the available data, the results. They observed that for none of the scales they assessed, a factor structure congruent with the use of the scales met all of their evaluation criteria, and reliability was rarely consistently above an acceptable threshold.

@@

As illustrated in the previous section, validating measurement is a complex but essential part of doing psychological research. Yet the scientific community has not fully stepped up to this challenge [@flakeMeasurementSchmeasurementQuestionable2020]. A large number of measures used in the psychological literature lack information on the validity and reliability of the measure [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022].

Questionable Measurement Practices (QMPs) are practices that raise doubts about a measurement’s validity [@flakeMeasurementSchmeasurementQuestionable2020] and have been coined as a term analogous to Questionable Research Practices [QRPs; @simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a]. QMPs range from lack of transparency in the reporting of the measure and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flakeMeasurementSchmeasurementQuestionable2020]. @flakeConstructValidityValidity2022 documented QMPs among 100 replications and their respective original articles from the Reproduciblity Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Additionally, only eight of the 40 translated scales contained validity evidence for the translated version. But reporting of reliability and validity evidence is not only low, but may also be biased as well. @husseyAberrantAbundanceCronbachs2023 observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and low reporting just below .70. Thus the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.

Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] also show that QMPs not only limit the reported validity of a measurement in a study, the lack of information also creates challenges for replicating researchers. Basic content descriptions such as the number of items, the response format, the scoring of the scale were irregular (!!!exact numbers!!!). If it is not clear what items were used, how they were scored, and how they were administered, then it is challenging to reconstruct the measurement for a replication study. In turn, the replication may assess the constructs in a substantially similar way, or they even assess different constructs. If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original. If constructs are assessed differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study. In either case, substantial comparisons between original and replication are hindered.

@@

Our aim is to provide a descriptive account of the reliability, validity, and reporting practices of measurement in replications and related original research. We coded several aspects of the measurement reporting practices in replications and original articles. Additionally, we estimated the reliability and validity evidence using openly available replication data of the measurement item responses from across multiple labs. Our unique contribution is by evaluating reported and the recalculated measurement information for each measure together. This allows us to capture a "double whammy" scenario where there is uncertainty in the reliability and validity of these measures when we calculate these ourselves, and where QMPs obscure the ability to evaluate the measure as well as inhibiting future researchers to recreate the measurement to validate it in a new study. Besides this, our study also functions as a conceptual replication of earlier research looking at reporting practices and measurement validation using different questions and analyses on a different set of replications and original research. While the theory underlying the measurement is important to evaluate how the content of the measure fits to the constructs of interest, because evaluating the theory of a measurement requires domain specific knowledge for each measure we do not address it in this study, we refer interested readers to articles discussing theory in measurement elsewhere [@gehlbachMeasureTwiceCut2011; @humphryPsychologicalMeasurementTheory2017; @borgstedeMeaningfulMeasurementRequires2023; @hasselmanGoingSquaresTheorybased2023].

# Disclosures

## Preregistration
We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>. We deviated from our coding protocol as is explained further in the text. Our pre-registered analyses have been move to the [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd) in favor of focusing on the descriptive results.

## Data, Materials, and Online Resources
TThis manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @R-worcs] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/> (DOI: 10.17605/OSF.IO/9R8YT).

## Reporting
We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was predetermined by the number of studies in the Many Labs projects.

## Ethical Approval
This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board (nr. TSB_TP_REMA06).

@@

The data consists of three main sources: replication datasets, replication protocols, and original study articles. We retrieved the data of Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages. Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosbyWhereWeLook2008a] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.

@@

### Saving to Intermediate Data Folder
saving_to_intermediate_data(data_1.3_clean)
saving_to_intermediate_data(data_1.10_clean)
saving_to_intermediate_data(data_1.11_clean)
saving_to_intermediate_data(data_1.12.3.1_clean)
saving_to_intermediate_data(data_1.12.3.2_clean)
saving_to_intermediate_data(data_2.10.1_clean)
saving_to_intermediate_data(data_2.12.1_clean)
saving_to_intermediate_data(data_2.12.2_clean)
saving_to_intermediate_data(data_2.12.3_clean)
saving_to_intermediate_data(data_2.15_clean)
saving_to_intermediate_data(data_2.20_clean)
saving_to_intermediate_data(data_2.23_clean)
saving_to_intermediate_data(data_3.2.1.1_clean)
saving_to_intermediate_data(data_3.2.1.2_clean)
saving_to_intermediate_data(data_3.7.1_clean)
saving_to_intermediate_data(data_3.7.2_clean)
saving_to_intermediate_data(data_3.8.2_clean)
saving_to_intermediate_data(data_5.1.1_clean)
saving_to_intermediate_data(data_5.1.2_clean)
saving_to_intermediate_data(data_5.4_clean)
saving_to_intermediate_data(data_5.7_clean)
saving_to_intermediate_data(data_5.9.1_clean)

@@

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of the replication of an original study. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).

@@

We extracted reported measurement information from the original articles and replication protocols using our preregistered coding protocol. We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) when present. Similarly, we coded if any psychometric construct validity evidence, such as a factor analysis, was presented for the measure. We additionally included twenty items that were based on the QMP table presented in @flakeMeasurementSchmeasurementQuestionable2020. For each of these items we a piece information we would want to see reported with regards to the measurement was described. If the information was clearly reported we coded the item as true; false if not or not clear enough; or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures). Example items can be seen in Table \@ref(tab:QMPCodingInfoTable).

@@

After the initial coding, we made minor revisions to 14 of the 20 QMP items from the preregistered coding protocol. These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent in the exact way and degree of detail in which to present things. For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables, and figures presented in this article are all based on the revised coding protocol. The equivalent QMP descriptives obtained with the initial protocol can be found in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_ratio_table.rmd).

We initially intended to form a QMP index using these QMP items and perform regression analyses using this index, but this index could not be validated properly and its results would be misleading to present here. A more detailed explanation of what was omitted and why, as well as the results from the preregistered analyses themselves can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd). The items are currently used as individual descriptives on the reporting practices in our sample.

@@

We calculated reliability for each measure from the replication datasets with suitable data for each lab the measure was used in. We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from @duhachekAlphasStandardError2004a to calculate the standard error in the meta-analysis. Then we entered these two values into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998]. Using RG Meta-Analysis we quantified the degree of true variation (or heterogeneity) in reliability coefficients across lab locations. We performed the RG Meta-Analysis using the rma function from the metafor R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor] and default settings. We evaluated the heterogeneity using the tau statistic and the Cochran's Q-test [@cochranCombinationEstimatesDifferent1954]. These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low [@hoaglinMisunderstandingsCochransTest2016; @pereiraCriticalInterpretationCochrans2010]. Therefore, we also present the prediction interval and suggest that the heterogeneity results should be viewed with a critical eye [@borensteinAvoidingCommonMistakes2024]. We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

Our analyses will focus on Cronbach’s Alpha, because its common use in research allows us to make comparisons between calculated and reported reliabilities. Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis. We additionally estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha, while also simultaneously providing some validity evidence [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017]. McDonald’s Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1. No RG Meta-Analysis was performed on McDonald's Omega, as we could not find a formula for calculating its standard error.

@@

We tested for unidimensionality using two tests on the data from each lab for each measure. If at least one of these tests was passed, the measure in that lab was marked as unidimensional. For the first test we fit a Confirmatory Factor Analysis (CFA) model with one factor to the data, and we then evaluate the RMSEA value. If this value is below .08, the test is passed. For the second test we run a parallel analysis. This runs multiple Exploratory Factor Analyses (EFA) where the number of factors in the model is increased by 1 until the number of factors is one less than the number of items. It then compares the eigenvalues (an indication of how much variance is explained by that factor) of each factor to the eigenvalues for that factor if the data matrix was effectively random. If only the single factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed. We chose a combination of these two tests, as the RMSEA is known to be biased for models with small degrees of freedom [@kennyPerformanceRMSEAModels2015], while the parallel analysis may be less suited if a two or more factor solution would also fit the sample item data.

@@

The average calculated Cronbach’s alpha coefficient across individual replications was `r apa_num(mean(calculated_reliability_lab_data$alpha))` with a standard deviation of `r apa_num(sd(calculated_reliability_lab_data$alpha))`. Figure \@ref(fig:PlotAlphaDistributions) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication, based on the meta-analytic p-value (alpha \< .05) retrieved from the Many Labs reports.

@@

```{r PlotAlphaDistributions, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated. Cronbach's alpha values that fell below 0 were excluded. The green lines indicate the meta-analytic prediction interval lower and upper bound. The blue triangles indicate the reported alpha coefficient for that measure from the original article, when reported. The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure. Meta-analyses for which the Q-test for heterogeneity was significant at alpha < .05 are in black, while non-significant results are in grey. The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures. The reported reliabilities that fell outside the 95% quantile of calculated reliability scores are shown in black, otherwise in grey."}
